---
title: "Automatic code hover with ch_hover()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Automatic code hover with ch_hover()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(ggplot2)
library(codehover)
```

Since version 2.0.0, `ch_hover()` is the main entry point of codehover.
Give it ggplot code and it:

1. splits the code at every top-level `+`;
2. evaluates each cumulative step;
3. renders one image per step;
4. returns a hoverable table with CSS and JavaScript attached — no
   template, YAML or jQuery needed.

# Basic use

```{r, echo=TRUE}
ch_hover({
  ggplot(cars, aes(x = speed, y = dist)) +
    geom_point(color = "red") +
    scale_y_continuous(limits = c(0, 100)) +
    labs(title = "A ggplot for the rest of us",
         subtitle = "Hover each row to see that step") +
    theme_bw()
}, width = 4, height = 3)
```

Hover the rows above: each one shows the plot as it looks *up to that
step*.

# Fixed scales

By default every step shows the true output of its partial code, so axes
and legends may move as layers are added. With `fixed_scales = TRUE` the
axes, legends and panel layout are pinned from the final plot, giving a
visually stable reveal (mechanism borrowed from the
[ggreveal](https://github.com/weverthonmachado/ggreveal) package):

```{r, echo=TRUE}
ch_hover({
  ggplot(mtcars, aes(x = wt, y = mpg)) +
    geom_point(aes(color = factor(cyl))) +
    geom_smooth(method = "lm")
}, fixed_scales = TRUE, width = 4, height = 3)
```

# Referencing a chunk by label

To keep your source document clean, write the plot in a normal chunk with
`eval=FALSE` and call `ch_hover_chunk()` with the chunk label:

```{r mybar, eval=FALSE, echo=TRUE}
ggplot(mtcars, aes(x = factor(cyl))) +
  geom_bar(fill = "steelblue") +
  coord_flip()
```

`r ch_hover_chunk("mybar", width = 4, height = 3)`

# Other options

* `type = "one_row"` highlights only the hovered row instead of the
  incremental effect.
* `path = "assets/"` keeps the step PNGs on disk and references them by
  relative path, instead of embedding base64 (smaller HTML, but the folder
  must travel with the page).
* `width`, `height` (inches) and `dpi` control the rendered images.

# When to use the manual API

`ch_hover()` handles ggplot `+` chains. For anything else — data-wrangling
pipelines, maps assembled from several objects, arbitrary images — use the
low-level `ch_int() %>% ch_row() %>% ch_out()` API described in the
introduction vignette.
